Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-10-04 GWLDCII.tex
new le diagram pictures, fixed incorrect arrow in section 5 fig

\usetikzlibrary{decorations.pathmorphing,calc}
\usetikzlibrary{intersections}

@@

 % used for showing which propagator assigns to which vertex in the last section
\pgfmathsetmacro{\arrowangle}{75}
\tikzstyle{propassignment} = [->,shorten >=2pt,thick]

@@

Recall that $I_1$ determines the shape of the Le diagram: specifically, the elements of $I_1$ label the rows of the diagram, working from top right to bottom left. By the arguments in Lemma {\ref{lem I}} we know that ${n,n-1,n-2, n-3 \not\in I_1^{V}}$.  These are the leftmost four columns of the diagram for $V$.  From Lemma \ref{lem I} we know that that $I_1^{W} = I_1^{V}\cup \{n-3\}$. Therefore, the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left. 
\end{proof}
\begin{figure}
  \[\includegraphics{Le_diagrams}\]
  \caption{Le diagrams for $V$ (left) and $W$ (right).}\label{fig Le}
\end{figure}

@@

\begin{figure}
\includegraphics[width=12cm]{new_le_diagrams.jpg}
\caption{The Le diagrams for $V$ and $W$ in the setting of Theorem~\ref{thm dim}. The shaded regions indicate where the plusses match up perfectly, the red plusses exist if and only if $n-2 \in I_{n-2}^V$, and the blue plusses are the three new plusses coming from the induction step.}\label{fig:le diagrams bijection}
\end{figure}

@@

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
\begin{scope}
	\drawWLDfragment[8]{3}{0.4} 
	%\drawnumberspartial % use this to debug
	\newnode[left]{1}{i-1}
	\newnode[below]{2}{i}
	\newnode[below]{7}{m}
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\newpropbend{1.7}{7.2}{60}
		\draw[smallpropagator,blue] (\zero+7.8*\step:\radius*1.1) to[bend left = 55] (\zero + 10*\step:\radius*1.1);
		\node at (\zero + 1.2*\step:\radius*0.5) {\footnotesize $p$};
	\end{scope}
	\node[align = center,black] at (\zero + \step*4.5:\radius*0.65) {\em \footnotesize propagators \\ \footnotesize \em inside $p$};
	\draw[propassignment,gray] (\zero + 1.6*\step:\radius) to[bend left = \arrowangle] (\zero + 1*\step:\radius); %p
	\draw[propassignment,gray] (\zero + 7.9*\step:\radius) to[bend left = \arrowangle] (\zero + 7*\step:\radius); 
	\node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $m \in I_i$ then \\ \em \footnotesize it was contributed by \\ \em \footnotesize the blue propagator};
\end{scope}
\end{tikzpicture}
\qquad 
\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
	\begin{scope}
	\drawWLDfragment[8]{3}{0.4}  
	%\drawnumberspartial % use this to debug
	\newnode[left]{1}{i}
	\newnode[below]{2}{i+1}
	\newnode[below]{7}{j}
	\centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 1.5*\step:\zero+1.56*\step:\radius);
	\draw[propassignment,gray] (\zero + 1.45*\step:\radius) to[bend left = \arrowangle] (\zero + 1*\step:\radius); %p
	\draw[propassignment,gray] (\zero + 1.61*\step:\radius) to[bend right = \arrowangle] (\zero + 2*\step:\radius); %q 
	\draw[propassignment,gray] (\zero + 7.7*\step:\radius) to[bend left = \arrowangle] (\zero + 7*\step:\radius); %blue
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\newpropbend{1.6}{7.2}{40} % q
		\draw[smallpropagator] (\zero+1.5*\step:\radius*1.1) to[bend right = 40] (\zero  - 3*\step:\radius*1.1); % p
		\draw[smallpropagator,blue] (\zero+7.6*\step:\radius*1.1) to[bend left = 55] (\zero + 10*\step:\radius*1.1);
		\node at (\zero + 5*\step:\radius*0.3) {\footnotesize $q$};
		\node at (\zero + 1*\step:\radius*0.6) {\footnotesize $p$};
	\end{scope}
	\node[align = center,black] at (\zero + \step*4.5:\radius*0.75) {\em \footnotesize propagators \\ \footnotesize \em inside $q$};
	\node[align = center] at (\zero + 1.5*\step:\radius*1.5) {\footnotesize \em No \\ \footnotesize \em propagators \\ \footnotesize \em between \\ \footnotesize \em $p$ and $q$ \\ \footnotesize \em here};
	\node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $j \in I_i$ then \\ \em \footnotesize it was contributed by \\ \em \footnotesize the blue propagator};
\end{scope}
\end{tikzpicture}
\]
  \caption{The two cases in the proof that no factors of $\Delta_{I_i}$ have degree 3 or more.{\color{violet}First picture: I thought $I_i(p) = i$. Doesn't the arrow say that $I_i(p) = i-1$?}}\label{fig no big factors}
\end{figure}

>>>>

\usetikzlibrary{calc} 
\usetikzlibrary{decorations.pathmorphing} % to get the wiggly propagator lines
\usetikzlibrary{bending} % to fix the arrow tips on bent lines
\usetikzlibrary{patterns} % for shading the Le diagrams in section 4

\newcommand{\leplus}{\Large $+$}
\newcommand{\lezero}{\Large $0$}

@@

 % used for showing which propagator assigns to which vertex in the last section
\pgfmathsetmacro{\arrowangle}{90}
\tikzstyle{propassignment} = [->,shorten >=2pt,thick]

@@

Recall that $I_1$ determines the shape of the Le diagram: specifically, the elements of $I_1$ label the rows of the diagram, working from top right to bottom left. By the arguments in Lemma {\ref{lem I}} we know that ${n,n-1,n-2, n-3 \not\in I_1^{V}}$.  These are the leftmost four columns of the diagram for $V$.  From Lemma \ref{lem I} we know that that $I_1^{W} = I_1^{V}\cup \{n-3\}$. Therefore, the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left. 
\end{proof}
\begin{figure}
  \[\begin{tikzpicture}[scale = 1.5]
\node at (1.5,2.5) {\Large $V$};
\draw (0,0) rectangle (1,2);
\draw (1,0) rectangle (1.3,2);
\begin{scope}[shift = {(-2.7,-2)}]
\draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (4,4);
\end{scope}
\node at (0.5,1) {\large$\mathcal{A}$};
\node at (1.8,1) {\large$\mathcal{B}$};
\begin{scope}[shift = {(5,0)}]
\node at (1.5,2.5) {\Large $W$};
\draw (0,-0.3) rectangle (1,0);
\draw (0,0) rectangle (1,2);
\begin{scope}[shift = {(-3,-2)}]
\draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (4,4);
\end{scope}
\node at (0.5,1) {\large$\mathcal{A}$};
\node at (1.5,1) {\large$\mathcal{B}$};
\end{scope}
\end{tikzpicture}\]
  \caption{Le diagrams for $V$ (left) and $W$ (right).}\label{fig Le}
\end{figure}

@@

\begin{figure}
\[
\begin{tikzpicture}[scale = 0.85]
\node at (2.5,5) {\Large $V$};
\node at (12.5,5) {\Large $W$};
\node at (-2,2.5) {\large $n-4 \in I_1^V$};
\node at (-2,-4.5) {\large $n-4 \not\in I_1^V$};
\node at (7.5,2.5) {\Large $\longrightarrow$};
\node at (8,-4.5) {\Large $\longrightarrow$};
% n-4 \in I_1, V
\begin{scope}
\draw[pattern color = gray,pattern = north east lines] (0,4) -- (0,2) -- (2,2) -- (2,4);
\draw[pattern color = gray,pattern = north west lines] (3,4) -- (3,0) -- (4,0) -- (4,4);
\draw (0,0) grid (4,2);
\foreach \x in {0,1,2,3,4} {
  \draw (\x,2) -- (\x,4);
  };
\foreach \c in {(0.5,0.5),(1.5,0.5),(1.5,1.5)} {
  \node at \c {\leplus};
}
\foreach \c in {(0.5,1.5),(2.5,1.5),(2.5,2.5)} {
  \node at \c {\lezero};
}
\node[red] at (2.5,0.5) {\leplus};
\node at (2.5,3.5) {$\vdots$};
\begin{scope}
\fill[pattern color = gray,pattern = horizontal lines] (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (4,4) -- (4,2);
\draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\end{scope}
%\fill[color = white,path fading = south] (0,2) rectangle (6.5,4.1);
\node[below] at (0.5,0) {\tiny $n\vphantom{1}$};
\node[below] at (1.5,0) {\tiny $n-1$};
\node[below] at (2.5,0) {\tiny $n-2$};
\node[below] at (3.5,0) {\tiny $n-3$};
\node[right] at (4,0.5) {\tiny $n-4$};
\node[right] at (4,1.5) {\tiny $n-5$};
\end{scope}

% n-4 \in I_1, W
\begin{scope}[shift = {(9,0)}]
\draw[pattern color = gray,pattern = north east lines] (0,4) -- (0,2) -- (2,2) -- (2,4);
\draw[pattern color = gray,pattern = north west lines] (2,4) -- (2,0) -- (3,0) -- (3,4);
\draw (0,-1) grid (3,2);
\foreach \x in {0,1,2,3} {
  \draw (\x,2) -- (\x,4);
  };
\foreach \c in {(0.5,0.5),(1.5,0.5),(1.5,1.5)} {
  \node at \c {\leplus};
}
\node[red] at (0.5,1.5) {\leplus};
\foreach \c in {(0.5,-0.5),(1.5,-0.5),(2.5,-0.5)} {
  \node[blue] at \c {\leplus};
}
\begin{scope}[shift = {(-1,0)}]
\fill[pattern color = gray,pattern = horizontal lines] (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (4,4) -- (4,2);
\draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\end{scope}
\node[below] at (0.5,-1) {\tiny $n\vphantom{1}$};
\node[below] at (1.5,-1) {\tiny $n-1$};
\node[below] at (2.5,-1) {\tiny $n-2$};
\node[right] at (3,-0.5) {\tiny $n-3$};
\node[right] at (3,0.5) {\tiny $n-4$};
\node[right] at (3,1.5) {\tiny $n-5$};
\end{scope}

% n-4 \not\in I_1, V
\begin{scope}[shift = {(0,-6)}]
\draw[pattern color = gray,pattern = north east lines] (0,3) -- (0,1) -- (2,1) -- (2,3);
\draw[pattern color = gray,pattern = north west lines] (3,3) -- (3,0) -- (4,0) -- (4,3);
\draw (0,0) grid (4,1);
\foreach \x in {0,1,2,3,4} {
  \draw (\x,1) -- (\x,3);
  };
\foreach \c in {(0.5,0.5),(1.5,0.5),(2.5,1.5)} {
  \node at \c {\lezero};
}
\node at (2.5,2.5) {$\vdots$};
\node[red] at (2.5,0.5) {\leplus};
\begin{scope}[shift = {(1,-1)}]
\fill[pattern color = gray,pattern = horizontal lines] (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (3,4) -- (3,1);
\draw (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\end{scope}

\node[below] at (0.5,0) {\tiny $n\vphantom{1}$};
\node[below] at (1.5,0) {\tiny $n-1$};
\node[below] at (2.5,0) {\tiny $n-2$};
\node[below] at (3.5,0) {\tiny $n-3$};
\node[below] at (4.5,0) {\tiny $n-4$};
\node[right] at (5,0.5) {\tiny $n-5$};
\end{scope}

% n-4 \not\in I_1, W
\begin{scope}[shift = {(9,-6)}]
\draw[pattern color = gray,pattern = north east lines] (0,3) -- (0,1) -- (2,1) -- (2,3);
\draw[pattern color = gray,pattern = north west lines] (2,3) -- (2,0) -- (3,0) -- (3,3);
\draw (0,-1) grid (3,1);
\foreach \x in {0,1,2,3} {
  \draw (\x,1) -- (\x,3);
  };
\node at (0.5,0.5) {\lezero};
\node[red] at (1.5,0.5) {\leplus};
\foreach \c in {(0.5,-0.5),(1.5,-0.5),(2.5,-0.5)} {
  \node[blue] at \c {\leplus};
}
\begin{scope}[shift = {(0,-1)}]
\fill[pattern color = gray,pattern = horizontal lines] (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (3,4) -- (3,1);
\draw (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
\end{scope}
\node[below] at (0.5,-1) {\tiny $n\vphantom{1}$};
\node[below] at (1.5,-1) {\tiny $n-1$};
\node[below] at (2.5,-1) {\tiny $n-2$};
\node at (3.5,-0.7) {\tiny $n-3$};
\node at (3.7,-0.2) {\tiny $n-4$};
\node[right] at (4,0.5) {\tiny $n-5$};
\end{scope}
\end{tikzpicture}
\]
\caption{The Le diagrams for $V$ and $W$ in the setting of Theorem~\ref{thm dim}. The shaded regions indicate where the plusses match up perfectly, the red plusses exist if and only if $n-2 \in I_{n-2}^V$, and the blue plusses are the three new plusses coming from the induction step.}\label{fig:le diagrams bijection}
\end{figure}

@@

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20,scale = 0.95]
\begin{scope}
  \drawWLDfragment[8]{3}{0.4} 
  %\drawnumberspartial % use this to debug
  \newnode[left]{1}{i-1}
  \newnode[below]{2.5}{i}
  \newnode[below]{7}{m}
  \begin{scope}
    \clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
    \newpropbend{1.9}{7.2}{60}
    \draw[smallpropagator,gray] (\zero+7.8*\step:\radius*1.1) to[bend left = 55] (\zero + 10*\step:\radius*1.1);
    \node at (\zero + 1.5*\step:\radius*0.5) {\footnotesize $p$};
  \end{scope}
  \node[align = center,black] at (\zero + \step*4.5:\radius*0.65) {\em \footnotesize propagators \\ \footnotesize \em inside $p$};
  \draw[propassignment,gray] (\zero + 1.81*\step:\radius) to[bend right = \arrowangle] (\zero + 2.5*\step:\radius); %p
  \draw[propassignment,gray] (\zero + 7.9*\step:\radius) to[bend left = \arrowangle] (\zero + 7*\step:\radius); 
  \node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $m \in I_i$ then it was \\ \em \footnotesize contributed by a propagator \\ \em \footnotesize outside of $p$};
  \node[align = center,black] at (110:\radius*0.5) {\em Case 1: $p = (i-1,m)$};
\end{scope}
\end{tikzpicture}
\qquad  
\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20,scale = 0.95]
  \begin{scope}
  \drawWLDfragment[8]{3}{0.4}  
  %\drawnumberspartial % use this to debug
  \newnode[left]{1}{i}
  \newnode[below]{2.5}{i+1\ \ \ }
  \newnode[below]{7}{j}
  \centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 1.61*\step:\zero+1.88*\step:\radius);
  \draw[propassignment,gray] (\zero + 1.55*\step:\radius) to[bend left = \arrowangle] (\zero + 1*\step:\radius); %p
  \draw[propassignment,gray] (\zero + 1.93*\step:\radius) to[bend right = \arrowangle] (\zero + 2.5*\step:\radius); %q 
  \draw[propassignment,gray] (\zero + 7.7*\step:\radius) to[bend left = \arrowangle] (\zero + 7*\step:\radius); % other prop
  \begin{scope}
    \clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
    \newpropbend{1.9}{7.2}{40} % q
    \draw[smallpropagator] (\zero+1.6*\step:\radius*1.1) to[bend right = 40] (\zero  - 3*\step:\radius*1.1); % p
    \draw[smallpropagator,gray] (\zero+7.6*\step:\radius*1.1) to[bend left = 55] (\zero + 10*\step:\radius*1.1);
    \node at (\zero + 5*\step:\radius*0.32) {\footnotesize $q$};
    \node at (\zero + 1.1*\step:\radius*0.6) {\footnotesize $p$};
  \end{scope}
  \node[align = center,black] at (\zero + \step*4.5:\radius*0.72) {\em \footnotesize propagators \\ \footnotesize \em inside $q$};
  \node[align = center] at (\zero + 1.8*\step:\radius*1.5) {\footnotesize \em No \\ \footnotesize \em propagators \\ \footnotesize \em between \\ \footnotesize \em $p$ and $q$ \\ \footnotesize \em here};
  \node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $j \in I_i$ then it was \\ \em \footnotesize contributed by a propagator \\ \em \footnotesize outside of $q$};
    \node[align = center,black] at (110:\radius*0.5) {\em Case 2: $p = (i,j)$};

\end{scope}
\end{tikzpicture}
\]
  \caption{The two cases in the proof that no factors of $\Delta_{I_i}$ have degree 3 or more.}\label{fig no big factors}
\end{figure}
